%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\usepackage{geometry}

\makeatletter
\let\@@outputpage\@outputpage
\def\@outputpage{\expandafter\@thisgeometry\@@outputpage}
\def\oddgeometryeven#1#2{%
	\gdef\@thisgeometry{%
		\ifnum\value{page}=1
		\newgeometry{left=6.1cm,top=2cm,right=1.5cm,bottom=2.5cm,nohead,nofoot}%
		\else
		\newgeometry{left=3.1cm,top=1.5cm,right=0.1cm,bottom=0.1cm,nohead,nofoot}%
		\fi}
}
\makeatother

\oddgeometryeven{left=6.1cm,top=2cm,right=1.5cm,bottom=2.5cm,nohead,nofoot}{left=3.1cm,top=1cm,right=0.1cm,bottom=0.1cm,nohead,nofoot}



\begin{document}
\header{Özer }{Özdal}
       {Ph.D. Candidate}


% In the aside, each new line forces a line break
\begin{aside}
  \section{Contact Information}
    Concordia University
    Loyola Campus
    Department of Physics SP 365.18
    7141 Sherbrooke Street West
    Montreal, QC  H4B 1R6
    Canada
    ~
    Tel: +1 438 927 73 00
    \href{mailto:ozerozdal@gmail.com}{ozerozdal@gmail.com}
    \href{http://www.linkedin.com/in/ozerozdal/}{linkedin://ozerozdal}
  %  \href{http://facebook.com/ozerozdal}{fb://ozerozdal}
    \href{http://github.com/oozdal}{github://oozdal}
  \section{Personal Information}
  	Date of birth 28/05/1990
  	Place of birth
  	Izmir, Turkey
  \section{Languages}
    Native Turkish
    Advanced English 
    Beginner French
  \section{Programming}
    $\textsc{Fortran}$, $\textsc{Python}$, 
    $\textsc{Matlab}$, $\textsc{C++}$,
    Bash shell scripting,
    $\textsc{Mathematica}$, LaTeX
\end{aside}

\section{Research interests}

Particle Physics Phenomenology \\
Beyond the Standard Model Phenomenology \\
Supersymmetric Extensions of the Standard Model \\
Dark Matter in Supersymmetric and Non-supersymmetric Models \\
LHC Phenomenology \\
Grand Unified Theories \\
Electroweak Symmetry Breaking \\

\section{Education}
\begin{entrylist}
	   \entry
	{2019-2020}
	{Visiting Ph.D. Student}
	{NExT Institute \& University of Southampton}
	{\emph{Compressed Supersymmetric Spectra at the Large Hadron Collider (LHC)} \\
		Host Supervisor: Prof. Stefano Moretti}
  \entry
    {since 2016}
    {Ph.D. candidate in Physics}
    {Concordia University}
    {\emph{Beyond Standard Model scenarios at LHC: dark matter, W' \& Z' mass limits}}
   \entry
   {2016--2017}
   {Inter-University Transfer Student}
   {McGill University}
   {\emph{Physics 610 Quantum Field Theory I given by Prof. Simon Caron-Huot \\
      Physics 673 Quantum Field Theory II given by Prof. Alexander Maloney }}
   
  \entry
    {2014–2016}
    {M.Sc. in Physics}
    {Izmir Institute of Technology}
    {\emph{The Higgs boson and right-handed neutrinos in supersymmetric models}}
  \entry
    {2009–2014}
    {B.Sc. in Physics (Ranked 3rd)}
    {Izmir Institute of Technology}
    {\emph{Revisiting N-symmetric barrier tunneling in Quantum Mechanics}}
    

\end{entrylist}

\section{Experience}

\begin{entrylist}
  \entry
    {Since 2016}
    {Concordia University}
    {Teaching Assistant (TA)}
    {\emph{
    PHYS 204: Mechanics (Tutor, 2019 Summer) \\    		
    PHYS 367: Modern Physics and Relativity (Tutor, 2019 Winter) \\		
    PHYS 245: Classical Mechanics (Tutor, 2018 Fall) \\
	PHYS 224: Introductory Experimental Mechanics (Lab Assistant) \\    		
    PHYS 252: Optics (2017 Winter, 2018 Winter) \\ 
	PHYS 236: Numerical Analysis in Physics (2016 Fall, 2017 Fall) \\
	}}
  \entry
    {Since 2016}
    {Concordia University}
    {Research Fellow}
    {\emph{Mariana Frank Research Group}}
  \entry
    {2015--2016}
    {TUBITAK Project No: 114F461}
    {Research Fellow}
    {\emph{Muon Anomalous Magnetic Moment and Yukawa Quasi-Unification in \\ Supersymmetric Models \\
    		Under the supervision of Assoc. Prof. Cem Salih Ün}}  
  \entry
  	{2012--2012}
  	{Koç University, Mechanical Characterization Lab}
  	{Internship}
  	{\emph{Vibration modeling in nanowire resonators with mechanical coupling \\
  	 Under the supervision of Assoc. Prof. Erdem Alaca}}  
\end{entrylist}

\section{Publications}

\begin{entrylist}
	
	\entry
	{2019}
	{Natural Dark Matter and light bosons in an alternative left-right symmetric model}
	{\href{https://arxiv.org/pdf/1911.12883.pdf}{Submitted to JHEP}} 
	
	
	\entry
	{2019}
	{Relaxing LHC constraints on the W$_R$ mass}
	{\href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.99.035001}{Phys. Rev. D 99, 035001}} 
	
	
	\entry
	{2018}
	{Exploring the supersymmetric U(1)$_{B-L} \times$ U(1)$_R$ model with dark matter, muon g−2, and Z' mass limits}
	{\href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.97.015012}{Phys. Rev. D 97, 015012}} 
	
	\entry
	{2017}
	{Muon g−2 in an alternative quasi-Yukawa unification with a less fine-tuned seesaw mechanism}
	{\href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.97.055007}{Phys. Rev. D 97, 055007}} 
	
	\entry
	{2016}
	{The Higgs boson and right-handed neutrinos in supersymmetric \\ models}
	{\href{http://openaccess.iyte.edu.tr/xmlui/handle/11147/2842}{IZTECH Theses \& Dissertations}} 
	
	\entry
	{2016}
	{Mass spectrum and Higgs profile in B−L symmetric SSM}
	{\href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.93.055024}{Phys. Rev. D 93, 055024}} 
	
\end{entrylist}

\section{Activities}

\begin{entrylist}		 	
	\entry
	{2015}
	{Introduction to Supersymmetry  Summer School \\ \normalfont (2015, September 7-11)}
	{\href{http://fezagursey.boun.edu.tr/?sayfa=29}{Boğaziçi University}}
	
	\entry
	{2015}
	{METU HEP Days  \normalfont (2015, February 12-14)}
	{\href{http://yef.ankara.edu.tr/yefgunleri2015/index.html}{METU}}
	
	\entry
	{2014}
	{Cosmology and Astroparticle Physics Summer School \\ \normalfont (2014, September 1-12)}
	{\href{http://fezagursey.boun.edu.tr/?sayfa=33}{Boğaziçi University}}
	
	\entry
	{2014}
	{Differential Geometry and Topological Methods in Physics Summer School  \normalfont (2014, August 25-29)}
	{\href{http://fezagursey.boun.edu.tr/?sayfa=32}{Boğaziçi University}}
	
	\entry
	{2014}
	{Computational Techniques for Physicists and Astronomers Summer School  \normalfont (2014, August 13-22)}
	{\href{http://fezagursey.boun.edu.tr/?sayfa=31}{Boğaziçi University}}
	
	\entry
	{2014}
	{Winter School on Computer Applications in Accelerator and Particle Physics \normalfont (2014, February 3-10)}
	{\href{http://hpfbu.web.cern.ch/hpfbu/HPFBU2014/HPFBU2014.html}{Gaziosmanpaşa University}}
	
	\entry
	{2013}
	{Physics for Astronomers \normalfont (2013, September 2-6)}
	{\href{http://fezagursey.boun.edu.tr/?sayfa=36}{Boğaziçi University}}
	
	\entry
	{2013}
	{Cosmology Summer School \normalfont (2013, August 19-30)}
	{\href{http://fezagursey.boun.edu.tr/?sayfa=35}{Boğaziçi University}}
	
	\entry
	{2010}
	{Istanbul University 27th International Physics  Congress \\ \normalfont (2010, September 14-17)}
	{\href{http://www.tfd.com.tr/arsiv/TFD/27/Wc9f53756aa549.htm}{Istanbul University}}
	
\end{entrylist}

\newpage

\section{Presentations}

\begin{entrylist}
	
	\entry
	{2019}
	{University of Southampton \normalfont (Oral Presentation) (2019, November 26) \\
		Title: Relaxing LHC constraints on the $W^\prime$ mass, and natural Dark Matter }
	{\href{https://www.hep.phys.soton.ac.uk/content/Tuesday-2019-11-26-Ozer-Ozdal}{University of Southampton}} 	
	
	\entry
	{2019}
	{NExT Meeting at Sussex \normalfont (Oral Presentation) (2019, November 20) \\
	Title: $W^\prime$ models at the LHC}
	{\href{https://indico.cern.ch/event/857401/overview}{University of Sussex}} 		
	
	
	\entry
	{2019}
	{Higgs Couplings Workshop, Oxford, UK \normalfont (Oral Presentation) (2019, September 30 - October 4) \\
		Title: Mass spectrum and Higgs profile in B-L symmetric SSM}
	{\href{https://indico.cern.ch/event/796574/contributions/3521711/}{Higgs Couplings 2019}} 	
	
	
	\entry
	{2019}
	{2019 XIth International Symposium: Quantum Theory and Symmetries (QTS)  \normalfont (Oral Presentation) (2019, 1-5 July) \\
		Title: Relaxing LHC constraints on the W$_R$ mass}
	{\href{http://www.crm.umontreal.ca/2019/QTS2019/pdf/ozdal.pdf}{QTS 2019}} 
	
	\entry
	{2018}
	{2018 Phenomenology Symposium, Pittsburgh, USA  \normalfont (Oral Presentation) \\ (2018, 7-9 May) \\
		Title: Naturalness and dark matter in supersymmetric U(1)$_{B-L} \times$ U(1)$_R$ \\ model}
	{\href{https://indico.cern.ch/event/699148/}{Pheno 2018}} 
	
	\entry
	{2018}
	{Winter Nuclear and Particle Physics Conference  \normalfont (Oral Presentation) \\ (2018, 15-18 February) \\
		Title: Exploring the supersymmetric U(1)$_{B-L} \times$ U(1)$_R$ model}
	{\href{http://wnppc.triumf.ca/2018/}{WNPPC 2018}}
	
	\entry
	{2015}
	{First Joint METU-IPM Conference on LHC Physics  \normalfont (Poster presentation) \\ (2015, September 29--October 3) \\
		Title: Higgs Anomalies in SUSY B-L Model}
	{\href{http://ictp-ecar.org/events/first-joint-metu-ipm-conference-on-lhc-physics/}{ICTP-ECAR}}
	
	\entry
	{2014}
	{Turkish Physical Society 31th International Physics Congress \\ \normalfont (Poster presentation - 2014, July 21-24) \\
		Title: Revisiting N-symmetric barrier tunneling in Quantum Mechanics}
	{\href{http://www.tfd.com.tr/arsiv/TFD/31/en/default.htm}{TFD-31}}
	
	\entry
	{2014}
	{Izmir Solid State Physics Meeting  \normalfont (Poster presentation) \\ (2014, April 11) \\
		Title: Revisiting N-symmetric barrier tunneling in Quantum Mechanics}
	{\href{http://ymf.iyte.edu.tr/?page_id=234}{IZTECH}}
	
	
\end{entrylist}







\section{On-going Studies}

\begin{entrylist}
	
		\entry
{1)}
{Compressed supersymmetric spectra at Large Hadron Collider \\ \normalfont
	Collaboration with Prof. Stefano Moretti and Prof. Mariana Frank}
{\href{https://www.mitacs.ca/en/programs/globalink/globalink-research-award}{}} 
	
		\entry
{2)}
{Correlating $W^\prime$ and $Z^\prime$ gauge boson mass limits in general \\ extensions of the Standard Model \\ \normalfont
	Collaboration with Prof. Benjamin Fuks, Prof. Stefano Moretti, Prof. Poulose Poulose and Prof. Mariana Frank}
{\href{https://www.mitacs.ca/en/programs/globalink/globalink-research-award}{}} 
	
\end{entrylist}	



\newpage

\section{Awards}

\begin{entrylist}
	
\entry
{2019}
{Mitacs Globalink Research Award}
{\href{https://www.mitacs.ca/en/programs/globalink/globalink-research-award}{Mitacs}} 	
	
	
%\entry
%{2019}
%{Graduate Student Mobility Award}
%{\href{https://www.concordia.ca/students/exchanges/funding/graduate-mobility-award.html}{Concordia University}} 	


\entry
{2016}
{Concordia International Tuition Award of Excellence}
{\href{http://www.concordia.ca}{Concordia University}} 	


\entry
{2014}
{B.Sc. in Physics 3rd Ranked Award}
{\href{http://www.iyte.edu.tr/AnaSayfa.aspx?d=ENG}{Izmir Institute of Technology}} 	
	
	
\end{entrylist}	
	

\section{References}
	
	\begin{entrylist}
		
		\entry
		{1)}
		{Prof. Mariana Frank \\ \normalfont
		Professor in Physics \\
		Office: 	L-SP 367-19 \\
		Richard J. Renaud Science Complex, 7141 Sherbrooke W. 	\\
		Office Phone: 	(514) 848-2424 ext. 3283 \\
		Concordia University}
		{\href{mariana.frank@concordia.ca}{mariana.frank@concordia.ca}} 
		

			
		\entry
		{2)}
		{Prof. Benjamin Fuks \\ \normalfont
		Professor in Physics \\	
		Laboratoire de Physique Théorique et Hautes Énergies (LPTHE) \\	
		Office : 	13-14.521 \\
		Office Phone: 	01 44 27 63 38	\\
		Sorbonne Université}
		{\href{fuks@lpthe.jussieu.fr}{fuks@lpthe.jussieu.fr}} 		
	
	    \entry
		{3)}
		{Prof. Stefano Moretti  \\ \normalfont
		Professor in Physics \\	
		School of Physics and Astronomy \\
		University of Southampton \\
		Highfield, Southampton SO17 1BJ, UK	\\
		Office Phone: 	+44 (0)23 8059 6829 \\
		University of Southampton}
		{\href{S.Moretti@soton.ac.uk}{S.Moretti@soton.ac.uk}} 			
	
		\entry
		{4)}
		{Prof. Poulose Poulose \\ \normalfont
		Associate Professor in Physics \\		
		Department of Physics \\
		IIT Guwahati, Assam 781039 \\
		Office Phone: +91 (0)361 2582713 \\			
		Indian Institute of Technology Guwahati}
		{\href{poulose@iitg.ac.in}{poulose@iitg.ac.in}} 					

	
	    \entry
		{5)}
		{Assoc. Prof. Cem Salih Ün  \\ \normalfont
		Associate Professor in Physics \\		
		Department of Physics \\			
		Uludağ University}
		{\href{cemsalihun@uludag.edu.tr}{cemsalihun@uludag.edu.tr}} 		

	    \entry
		{6)}
		{Prof. Durmuş Ali Demir  \\ \normalfont
		Professor in Physics \\		
		Department of Physics \\
	    Office Phone: +90 216 568 7042 \\						
		Sabancı University}
		{\href{durmus.demir@sabanciuniv.edu}{durmus.demir@sabanciuniv.edu}} 		


	\end{entrylist}

\end{document}
