%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}


\usepackage{lipsum}

\addbibresource{bibliography.bib}

\usepackage{geometry}

\makeatletter
\let\@@outputpage\@outputpage
\def\@outputpage{\expandafter\@thisgeometry\@@outputpage}
\def\oddgeometryeven#1#2{%
	\gdef\@thisgeometry{%
		\ifnum\value{page}=1
		\newgeometry{left=6.1cm,top=1.2cm,right=1.5cm,bottom=0.1cm,nohead,nofoot}%
		\else
        \newgeometry{left=3.1cm,top=1.5cm,right=1.5cm,bottom=0.1cm,nohead,nofoot}%
		\fi}
}
\makeatother

\oddgeometryeven{left=6.1cm,top=2cm,right=1.5cm,bottom=2.5cm,nohead,nofoot}{left=3.1cm,top=1cm,right=0.1cm,bottom=0.1cm,nohead,nofoot}



\begin{document}
\header {Özer Özdal}
    %   {Ph.D.}


% In the aside, each new line forces a line break
\begin{aside}
	\section{Contact Information}
	Tel: +1 438 935 74 64
	\href{mailto:ozerozdal@gmail.com}{ozerozdal@gmail.com}
	\href{http://www.linkedin.com/in/ozerozdal/}{linkedin://ozerozdal}
	%  \href{http://facebook.com/ozerozdal}{fb://ozerozdal}
	\href{http://github.com/oozdal}{github://oozdal}
	\section{Personal Information}
	\bullet Date of birth 
	28/05/1990
	\bullet Place of birth
	Izmir, Turkey
	\section{Languages}
	Native Turkish
	Advanced English 
	French (A2 Level)
	\section{Software Skills}
	Monte Carlo Sampling
	Statistical Modeling
	Linear regression
	Clustering     
	Quantitative Analysis    
	Data Visualization
	\section{Coursework}  
	\bullet Machine Learning
	\bullet Deep Learning Specialization
	\bullet SQL for Data Science
	\bullet Linear Algebra
	\bullet Multivariate Calculus
	\bullet Probability Theory
	\bullet Computational Physics    
	\bullet Classical Mechanics
	\bullet Quantum Mechanics
	\bullet Statistical Mechanics
	\section{Tools}
	$\textsc{Python}$, $\textsc{C++}$ 
	$\textsc{SQL}$, $\textsc{Fortran}$
	$\textsc{CERN ROOT}$, LaTeX   
	Bash shell scripting
	$\textsc{Mathematica}$,  $\textsc{Matlab}$
	\section{Packages}  
	Scikit-Learn,
	NumPy, SciPy,
	Pandas, Matplotlib,
	Pytorch, TensorFlow    
\end{aside}



\section{Research interests}

Particle Physics Phenomenology, Beyond the Standard Model Phenomenology, \\
Supersymmetry, Dark Matter, LHC Phenomenology/Collider Physics, \\
Computing Tools for High-Energy Physics, Future High-Energy Physics Experiments, \\
Grand Unified Theories (GUT), Electroweak Symmetry Breaking \\

\section{Education}
\begin{entrylist}
  \entry
    {2016--2020}
    {Ph.D. in Physics}
    {Concordia University}
    {\emph{Phenomenology of new physics beyond the Standard Model: signals of dark matter and new gauge bosons at colliders. Lead to five scientific publications.}}
   \entry
   {2016--2017}
   {Inter-University Transfer Student}
   {McGill University}
   {\emph{Took two graduate courses: \\
      Physics 610 Quantum Field Theory I given by Prof. Simon Caron-Huot \\
      Physics 673 Quantum Field Theory II given by Prof. Alexander Maloney }}
   
  \entry
    {2014–2016}
    {M.Sc. in Physics}
    {Izmir Institute of Technology}
    {\emph{The Higgs boson and right-handed neutrinos in supersymmetric models. Lead to two scientific publications.}}
  \entry
    {2009–2014}
    {B.Sc. in Physics (Ranked 3rd)}
    {Izmir Institute of Technology}
    {\emph{Revisiting N-symmetric barrier tunneling in Quantum Mechanics}}
    

\end{entrylist}

\section{Experience}

\begin{entrylist}
    \entry
	{since 2020}
	{Postdoctoral Researcher (PD)}
	{Concordia University}
    {\emph{Mariana Frank Research Group}}		
    \entry
	{2016--2020}
	{Research Assistant (RA)}
	{Concordia University}
	{\emph{Mariana Frank Research Group}}	
	 \entry
    {2019-2020}
    {Visiting Ph.D. Student}
    {NExT Institute \& University of Southampton}
    {\emph {Supported by MITACS Globalink Research Award. Lead to two scientific \\ publications.}}
    \entry
    {2016-2020}
    {Teaching Assistant (TA)}
    {Concordia University}
    {\emph{
    TAed for 8 physics courses. Graded assignments and wrote solutions, lead office hours and tutorial sessions: \\
    PHYS 273: Energy and Environment (2020 Winter) \\		
    PHYS 284: Introduction to Astronomy (2019 Fall) \\
    PHYS 204: Mechanics (Tutor, 2019 Summer, 2020 Summer) \\    		
    PHYS 367: Modern Physics and Relativity (Tutor, 2019 Winter) \\		
    PHYS 245: Classical Mechanics (Tutor, 2018 Fall) \\
	PHYS 224: Introductory Experimental Mechanics (Lab Assistant) \\    		
    PHYS 252: Optics (2017 Winter, 2018 Winter) \\ 
	PHYS 236: Numerical Analysis in Physics (2016 Fall, 2017 Fall) \\
	}}
    \entry
    {2015--2016}
    {Research Assistant (RA)}
    {TUBITAK Project No: 114F461}
    {\emph{Studied muon anomalous magnetic moment and yukawa quasi-unification \\ in supersymmetric Models. Lead to two scientific publications.}}  
    \entry
  	{2012--2012}
  	{Internship}
  	{Koç University, Mechanical Characterization Lab}
  	{\emph{Created vibration modeling in nanowire resonators with mechanical coupling }}  
\end{entrylist}

\newpage

\section{Publications}
\begin{entrylist}
	\entryp
	{2020}
	{Leptophobic $Z^\prime$ bosons in the secluded $U(1)^\prime$ model}
	{\href{https://arxiv.org/abs/2005.08472}{arXiv:2005.08472}} 	
	
	\entryp
	{2020}
	{E6 motivated UMSSM confronts experimental data}
	{\href{https://doi.org/10.1007/JHEP05(2020)123}{J. High Energ. Phys. 2020, 123 (2020)}} 	
	
	\entryp
	{2019}
	{Natural Dark Matter and light bosons in an alternative left-right symmetric model \\}
	{\href{https://doi.org/10.1007/JHEP04(2020)116}{J. High Energ. Phys. 2020, 116 (2020)}} 
	
	\entryp
	{2019}
	{Relaxing LHC constraints on the W$_R$ mass}
	{\href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.99.035001}{Phys. Rev. D 99, 035001}} 
	
	\entryLongTitle
	{2018}
	{Exploring the supersymmetric U(1)$_{B-L} \times$ U(1)$_R$ model}{with dark matter, muon g−2, and $Z^\prime$ mass limits}
	{\href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.97.015012}{Phys. Rev. D 97, 015012}} 
	
	\entryLongTitle
	{2017}
	{Muon g−2 in an alternative quasi-Yukawa unification}{with a less fine-tuned seesaw mechanism}
	{\href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.97.055007}{Phys. Rev. D 97, 055007}} 
	
	\entryp
	{2016}
	{The Higgs boson and right-handed neutrinos in supersymmetric models \\}
	{\href{http://openaccess.iyte.edu.tr/xmlui/handle/11147/2842}{IZTECH Theses \& Dissertations}} 
	
	\entryp
	{2016}
	{Mass spectrum and Higgs profile in B−L symmetric SSM}
	{\href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.93.055024}{Phys. Rev. D 93, 055024}} 
	
\end{entrylist}

\section{Activities}

\begin{entrylist}		 	
	\entryp
	{2020}
	{Beyond Standard Model: From Theory to Experiment \normalfont (2021, March)}
	{\href{https://indico.cern.ch/event/959266/}{BSM - 2021}}	
	

	\entryp
	{2015}
	{Introduction to Supersymmetry  Summer School \normalfont (2015, September 7-11)}
	{\href{http://fezagursey.boun.edu.tr/?sayfa=29}{Boğaziçi University}}
	
	\entryp
	{2015}
	{METU HEP Days  \normalfont (2015, February 12-14)}
	{\href{http://yef.ankara.edu.tr/yefgunleri2015/index.html}{METU}}
	
	\entryp
	{2014}
	{Cosmology and Astroparticle Physics Summer School \normalfont (2014, September 1-12) \\}
	{\href{http://fezagursey.boun.edu.tr/?sayfa=33}{Boğaziçi University}}
	
	\entryp
	{2014}
	{Differential Geometry and Topological Methods in Physics Summer School \\}
	{\href{http://fezagursey.boun.edu.tr/?sayfa=32}{Boğaziçi University}}
	
	\entryp
	{2014}
	{Computational Techniques for Physicists and Astronomers Summer School \\}
	{\href{http://fezagursey.boun.edu.tr/?sayfa=31}{Boğaziçi University}}
	
	\entryp
	{2014}
	{Winter School on Computer Applications in Accelerator and Particle Physics \\}
	{\href{http://hpfbu.web.cern.ch/hpfbu/HPFBU2014/HPFBU2014.html}{Gaziosmanpaşa University}}
	
	\entryp
	{2013}
	{Physics for Astronomers \normalfont (2013, September 2-6)}
	{\href{http://fezagursey.boun.edu.tr/?sayfa=36}{Boğaziçi University}}
	
	\entryp
	{2013}
	{Cosmology Summer School \normalfont (2013, August 19-30)}
	{\href{http://fezagursey.boun.edu.tr/?sayfa=35}{Boğaziçi University}}
	
	\entryp
	{2010}
	{Istanbul University 27th International Physics  Congress}
	{\href{http://www.tfd.com.tr/arsiv/TFD/27/Wc9f53756aa549.htm}{Istanbul University}}
	
\end{entrylist}

\newpage

\section{Presentations}

\begin{entrylist}
	
	\entrySuperLong
	{2019}
	{University of Southampton \normalfont (Oral Presentation) (2019, November 26)}{Title: Relaxing LHC constraints on the $W^\prime$ mass, and natural Dark Matter} 
	{\href{https://www.hep.phys.soton.ac.uk/content/Tuesday-2019-11-26-Ozer-Ozdal}{University of Southampton}} 	
	
	\entrySuperLong
	{2019}
	{NExT Meeting at Sussex \normalfont (Oral Presentation) (2019, November 20)}
	{Title: $W^\prime$ searches at the LHC}
	{\href{https://indico.cern.ch/event/857401/overview}{University of Sussex}} 		
	
	\entrySuperLong
	{2019}
	{Higgs Couplings Workshop, Oxford, UK \normalfont (Oral Presentation) (September 30 - October 4)}
	{Title: Mass spectrum and Higgs profile in B-L symmetric SSM}
	{\href{https://indico.cern.ch/event/796574/contributions/3521711/}{Higgs Couplings 2019}} 	
		
	\entrySuperLong
	{2019}
	{XIth International Symposium: Quantum Theory and Symmetries (QTS)}
	{Title: Relaxing LHC constraints on the W$_R$ mass}
	{\href{http://www.crm.umontreal.ca/2019/QTS2019/pdf/ozdal.pdf}{QTS 2019}} 
	
	\entrySuperLong
	{2018}
	{Phenomenology Symposium, Pittsburgh, USA  \normalfont (Oral Presentation) (2018, 7-9 May)}
	{Title: Naturalness and dark matter in supersymmetric U(1)$_{B-L} \times$ U(1)$_R$ model}
	{\href{https://indico.cern.ch/event/699148/}{Pheno 2018}} 
	
	\entrySuperLong
	{2018}
	{Winter Nuclear and Particle Physics Conference  \normalfont (Oral Presentation) (2018, 15-18 February)}
	{Title: Exploring the supersymmetric U(1)$_{B-L} \times$ U(1)$_R$ model}
	{\href{http://wnppc.triumf.ca/2018/}{WNPPC 2018}}
	
	\entrySuperLong
	{2015}
	{First Joint METU-IPM Conference on LHC Physics  \normalfont (Poster) (September 29--October 3)}
	{Title: Higgs Anomalies in SUSY B-L Model}
	{\href{http://ictp-ecar.org/events/first-joint-metu-ipm-conference-on-lhc-physics/}{ICTP-ECAR}}
	
	\entrySuperLong
	{2014}
	{Turkish Physical Society 31th International Physics Congress \normalfont (Poster) (July 21-24)}
	{Title: Revisiting N-symmetric barrier tunneling in Quantum Mechanics}
	{\href{http://www.tfd.com.tr/arsiv/TFD/31/en/default.htm}{TFD-31}}
	
	\entrySuperLong
	{2014}
	{Izmir Solid State Physics Meeting  \normalfont (Poster) (2014, April 11)}
	{Title: Revisiting N-symmetric barrier tunneling in Quantum Mechanics}
	{\href{http://ymf.iyte.edu.tr/?page_id=234}{IZTECH}}
	
	
\end{entrylist}







\section{On-going Studies \& Future Plans}

\begin{entrylist}
	
	\entrySuperLong
{1)}
{Correlating $W^\prime$ and $Z^\prime$ mass limits in general extensions of the Standard Model}
{Collaboration with Prof. Benjamin Fuks, Prof. Stefano Moretti and Prof. Mariana Frank}
{\href{https://www.mitacs.ca/en/programs/globalink/globalink-research-award}{}} 

	\entrySuperLong
{2)}
{Complete detector analysis for wide $W^\prime \& Z^\prime$ searches}
{$W^\prime \to WZ$, $Z^\prime \to WW$, possibly also including Higgses ($V^\prime \to V h$)}
{\href{https://www.mitacs.ca/en/programs/globalink/globalink-research-award}{}} 
	
	\entrySuperLong
{3)}
{Explanation of electron and muon g − 2 anomalies in a single framework}
{}
{\href{https://www.mitacs.ca/en/programs/globalink/globalink-research-award}{}} 	
	
	
	\entrySuperLong
{4)}
{Long-lived particles at the LHC}
{}
{\href{https://www.mitacs.ca/en/programs/globalink/globalink-research-award}{}} 	
	
	\entrySuperLong
{5)}
{Dark matter characterization at the LHC}
{}
{\href{https://www.mitacs.ca/en/programs/globalink/globalink-research-award}{}} 		
	
	
\end{entrylist}	




\section{Awards}

\begin{entrylist}
	
\entryp
{2019}
{Mitacs Globalink Research Award}
{\href{https://www.mitacs.ca/en/programs/globalink/globalink-research-award}{Mitacs}} 	
	

\entryp
{2016}
{Concordia International Tuition Award of Excellence}
{\href{http://www.concordia.ca}{Concordia University}} 	


\entryp
{2014}
{B.Sc. in Physics 3rd Ranked Award}
{\href{http://www.iyte.edu.tr/AnaSayfa.aspx?d=ENG}{Izmir Institute of Technology}} 	
	
	
\end{entrylist}	

\newpage	

\section{References}
	
	\begin{entrylist}
		
		\entry
		{1)}
		{Prof. Mariana Frank \\ \normalfont
		Professor in Physics \\
		Office: 	L-SP 367-19 \\
		Richard J. Renaud Science Complex, 7141 Sherbrooke W. 	\\
		Office Phone: 	(514) 848-2424 ext. 3283 \\
		Concordia University}
		{\href{mariana.frank@concordia.ca}{mariana.frank@concordia.ca}} 
		

			
		\entry
		{2)}
		{Prof. Benjamin Fuks \\ \normalfont
		Professor in Physics \\	
		Laboratoire de Physique Théorique et Hautes Énergies (LPTHE) \\	
		Office : 	13-14.521 \\
		Office Phone: 	01 44 27 63 38	\\
		Sorbonne Université}
		{\href{fuks@lpthe.jussieu.fr}{fuks@lpthe.jussieu.fr}} 		
	
	    \entry
		{3)}
		{Prof. Stefano Moretti  \\ \normalfont
		Professor in Physics \\	
		School of Physics and Astronomy \\
		University of Southampton \\
		Highfield, Southampton SO17 1BJ, UK	\\
		Office Phone: 	+44 (0)23 8059 6829 \\
		University of Southampton}
		{\href{S.Moretti@soton.ac.uk}{S.Moretti@soton.ac.uk}} 			
	
		\entry
		{4)}
		{Prof. Poulose Poulose \\ \normalfont
		Associate Professor in Physics \\		
		Department of Physics \\
		IIT Guwahati, Assam 781039 \\
		Office Phone: +91 (0)361 2582713 \\			
		Indian Institute of Technology Guwahati}
		{\href{poulose@iitg.ac.in}{poulose@iitg.ac.in}} 					

	
	    \entry
		{5)}
		{Assoc. Prof. Cem Salih Ün  \\ \normalfont
		Associate Professor in Physics \\		
		Department of Physics \\			
		Uludağ University}
		{\href{cemsalihun@uludag.edu.tr}{cemsalihun@uludag.edu.tr}} 		

	    \entry
		{6)}
		{Prof. Durmuş Ali Demir  \\ \normalfont
		Professor in Physics \\		
		Department of Physics \\
	    Office Phone: +90 216 568 7042 \\						
		Sabancı University}
		{\href{durmus.demir@sabanciuniv.edu}{durmus.demir@sabanciuniv.edu}} 		


	\end{entrylist}






\end{document}
