%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}


\usepackage{lipsum}

\addbibresource{bibliography.bib}

\usepackage{geometry}

\makeatletter
\let\@@outputpage\@outputpage
\def\@outputpage{\expandafter\@thisgeometry\@@outputpage}
\def\oddgeometryeven#1#2{%
	\gdef\@thisgeometry{%
		\ifnum\value{page}=1
		\newgeometry{left=6.1cm,top=1.2cm,right=1.5cm,bottom=0.1cm,nohead,nofoot}%
		\else
        \newgeometry{left=3.1cm,top=1.5cm,right=1.5cm,bottom=0.1cm,nohead,nofoot}%
		\fi}
}
\makeatother

\oddgeometryeven{left=6.1cm,top=2cm,right=1.5cm,bottom=2.5cm,nohead,nofoot}{left=3.1cm,top=1cm,right=0.1cm,bottom=0.1cm,nohead,nofoot}



\begin{document}
\header {Özer Özdal}
    %   {Ph.D.}


% In the aside, each new line forces a line break
\begin{aside}
	\section{Contact Information}
	Tel: +1 438 935 74 64
	\href{mailto:ozerozdal@gmail.com}{ozerozdal@gmail.com}
	\href{http://www.linkedin.com/in/ozerozdal/}{linkedin://ozerozdal}
	%  \href{http://facebook.com/ozerozdal}{fb://ozerozdal}
	\href{http://github.com/oozdal}{github://oozdal}
	\section{Personal Information}
	\bullet Date of birth 
	28/05/1990
	\bullet Place of birth
	Izmir, Turkey
	\section{Languages}
	Native Turkish
	Advanced English 
	French (A2 Level)
	\section{Software Skills}
	Monte Carlo Sampling
	Statistical Modeling
	Linear regression
	Clustering     
	Quantitative Analysis    
	Data Visualization
	\section{Coursework}  
	\bullet Machine Learning
	\bullet Deep Learning Specialization
	\bullet SQL for Data Science
	\bullet Linear Algebra
	\bullet Multivariate Calculus
	\bullet Probability Theory
	\bullet Computational Physics    
	\bullet Classical Mechanics
	\bullet Quantum Mechanics
	\bullet Statistical Mechanics
	\section{Tools}
	$\textsc{Python}$, $\textsc{C++}$ 
	$\textsc{SQL}$, $\textsc{Fortran}$
	$\textsc{CERN ROOT}$, LaTeX   
	Bash shell scripting
	$\textsc{Mathematica}$,  $\textsc{Matlab}$
	\section{Packages}  
	Scikit-Learn,
	NumPy, SciPy,
	Pandas, Matplotlib,
	Pytorch, TensorFlow    
\end{aside}





\section{References}
	
	\begin{entrylist}
		
		\entry
		{1)}
		{Prof. Mariana Frank \\ \normalfont
		Professor in Physics \\
		Office: 	L-SP 367-19 \\
		Richard J. Renaud Science Complex, 7141 Sherbrooke W. 	\\
		Office Phone: 	(514) 848-2424 ext. 3283 \\
		Concordia University}
		{\href{mariana.frank@concordia.ca}{mariana.frank@concordia.ca}} 
		

			
		\entry
		{2)}
		{Prof. Benjamin Fuks \\ \normalfont
		Professor in Physics \\	
		Laboratoire de Physique Théorique et Hautes Énergies (LPTHE) \\	
		Office : 	13-14.521 \\
		Office Phone: 	01 44 27 63 38	\\
		Sorbonne Université}
		{\href{fuks@lpthe.jussieu.fr}{fuks@lpthe.jussieu.fr}} 		
	
	    \entry
		{3)}
		{Prof. Stefano Moretti  \\ \normalfont
		Professor in Physics \\	
		School of Physics and Astronomy \\
		University of Southampton \\
		Highfield, Southampton SO17 1BJ, UK	\\
		Office Phone: 	+44 (0)23 8059 6829 \\
		University of Southampton}
		{\href{S.Moretti@soton.ac.uk}{S.Moretti@soton.ac.uk}} 			
	
		\entry
		{4)}
		{Prof. Poulose Poulose \\ \normalfont
		Associate Professor in Physics \\		
		Department of Physics \\
		IIT Guwahati, Assam 781039 \\
		Office Phone: +91 (0)361 2582713 \\			
		Indian Institute of Technology Guwahati}
		{\href{poulose@iitg.ac.in}{poulose@iitg.ac.in}} 					

	
	    \entry
		{5)}
		{Assoc. Prof. Cem Salih Ün  \\ \normalfont
		Associate Professor in Physics \\		
		Department of Physics \\			
		Uludağ University}
		{\href{cemsalihun@uludag.edu.tr}{cemsalihun@uludag.edu.tr}} 		

	    \entry
		{6)}
		{Prof. Durmuş Ali Demir  \\ \normalfont
		Professor in Physics \\		
		Department of Physics \\
	    Office Phone: +90 216 568 7042 \\						
		Sabancı University}
		{\href{durmus.demir@sabanciuniv.edu}{durmus.demir@sabanciuniv.edu}} 		


	\end{entrylist}






\end{document}
