%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}


\usepackage{lipsum}
\usepackage{enumitem}

\addbibresource{bibliography.bib}

\usepackage{geometry}

\makeatletter
\let\@@outputpage\@outputpage
\def\@outputpage{\expandafter\@thisgeometry\@@outputpage}
\def\oddgeometryeven#1#2{%
	\gdef\@thisgeometry{%
		\ifnum\value{page}=1
		\newgeometry{left=6.1cm,top=1.2cm,right=1.5cm,bottom=0.1cm,nohead,nofoot}%
		\else
		\newgeometry{left=3.1cm,top=1.5cm,right=1.5cm,bottom=0.1cm,nohead,nofoot}%
		\fi}
}
\makeatother

\oddgeometryeven{left=6.1cm,top=1cm,right=1.5cm,bottom=0.1cm,nohead,nofoot}{left=3.1cm,top=1cm,right=0.1cm,bottom=0.1cm,nohead,nofoot}



\begin{document}
\header {Özer Özdal}
    %   {Ph.D.}


% In the aside, each new line forces a line break
\begin{aside}
  \section{Contact Information}
    Tel: +1 438 935 74 64
    \href{mailto:ozerozdal@gmail.com}{ozerozdal@gmail.com}
    \href{http://www.linkedin.com/in/ozerozdal/}{linkedin://ozerozdal}
  %  \href{http://facebook.com/ozerozdal}{fb://ozerozdal}
    \href{http://github.com/oozdal}{github://oozdal}
 	\href{https://inspirehep.net/author/profile/O.Ozdal.1}{iNSPIRE: O.Ozdal.1}   
  \section{Personal Information}
  	\bullet Date of birth 
  	28/05/1990
  	\bullet Place of birth
  	Izmir, Turkey
  \section{Languages}
    Native Turkish
    Advanced English 
    French (A2 Level)
  \section{Software Skills}
    Monte Carlo Sampling
    Statistical Modeling
    Linear regression
	Clustering     
    Quantitative Analysis    
    Data Visualization
  \section{Coursework}  
  \bullet Machine Learning
  \bullet Deep Learning Specialization
  \bullet SQL for Data Science
  \bullet Linear Algebra
  \bullet Multivariate Calculus
  \bullet Probability Theory
  \bullet Computational Physics    
  \bullet Classical Mechanics
  \bullet Quantum Mechanics
  \bullet Statistical Mechanics
    \section{Tools}
    $\textsc{Python}$, $\textsc{C++}$ 
    $\textsc{SQL}$, $\textsc{Fortran}$
    $\textsc{CERN ROOT}$, LaTeX   
    Bash shell scripting
    $\textsc{Mathematica}$,  $\textsc{Matlab}$
    \section{Packages}  
    Scikit-Learn,
    NumPy, SciPy,
    Pandas, Matplotlib,
    Pytorch, TensorFlow    
\end{aside}

\section{Data Science Experience}

\begin{entrylist}
	\entry
	{since 2018}
	{Machine Learning in High-Energy Physics}
	{Concordia University}
   {\emph{My goal is to compare two D dimensional samples: the SM simulated events (background to BSM searches), and the real data, and to check if the two are drawn from the same probability density distribution.}}

\end{entrylist}

\section{Education}
\begin{entrylist}
  \entry
    {2016--2020}
    {Ph.D. in Theoretical High Energy Physics}
    {Concordia University}
    {\emph{Phenomenology of new physics beyond the Standard Model: signals of dark matter and new gauge bosons at colliders. Lead to five scientific publications.}}
   \entry
   {2016--2017}
   {Inter-University Transfer Student}
   {McGill University}
   {\emph{Took two graduate courses: Quantum Field Theory I -  II}}
   
  \entry
    {2014–2016}
    {M.Sc. in Theoretical High Energy Physics}
    {Izmir Institute of Technology}
    {\emph{The Higgs boson and right-handed neutrinos in supersymmetric models. Lead to two scientific publications.}}
  \entry
    {2009–2014}
    {B.Sc. in Physics (Ranked 3rd)}
    {Izmir Institute of Technology}
    {\emph{Revisited N-symmetric barrier tunneling in Quantum Mechanics}}
    

\end{entrylist}

\section{Experience}

\begin{entrylist}
    \entry
	{2020--}
	{Postdoctoral Researcher}
	{Concordia University}
	{\emph{}}
    \entry
	{2016--2020}
	{Research Assistant (RA)}
	{Concordia University}
	{\emph{Mariana Frank Research Group}}	
	 \entry
    {2019-2020}
    {Visiting Ph.D. Student}
    {NExT Institute \& University of Southampton}
    {\emph {Supported by MITACS Globalink Research Award. Lead to two scientific \\ publications.}}
    \entry
    {2016-2020}
    {Teaching Assistant (TA)}
    {Concordia University}
    {\emph{
    		TAed for 8 physics courses. Graded assignments and wrote solutions, lead office hours and tutorial sessions.
	}}
    \entry
    {2015--2016}
    {Research Assistant (RA)}
    {TUBITAK}
    {\emph{Studied muon anomalous magnetic moment and yukawa quasi-unification \\ in supersymmetric Models. Lead to two scientific publications.}}  
    \entry
  	{2012--2012}
  	{Internship}
  	{Koç University, Mechanical Characterization Lab}
  	{\emph{Created vibration modeling in nanowire resonators with mechanical coupling}}  
\end{entrylist}


\section{Relevant  Accomplishments}

\begin{itemize}[topsep=0pt, partopsep=0pt]
		\item 7 peer-reviewed scientific publications in High Energy Physics 
		\item Gave 17 talks about my research at conferences
	    \item Awarded Globalink Research Award by MITACS and Graduate Student Mobility Award
		\item Attended 18 scientific workshops, summer/winter schools in top institutions	   
%		\item Awarded by Concordia International Tuition Award of Excellence
	    \item B.Sc. in Physics 3rd Ranked Award		 
\end{itemize}

\end{document}
